\documentclass{beamer}

%\documentclass[notes]{beamer}

\usepackage{inputenc}
\usepackage{graphicx}

\title{Slow and Steady: Measuring and Tuning Multicore Interference}
\subtitle{Dan Iorga, Tyler Sorenson, John Wickerson, Alastair Donaldson}

\author{Presented by: Akshay Gopalakrishnan}

\begin{document}
    
    \begin{frame}

        \titlepage
    
    \end{frame}

    \begin{frame}{Introduction}

        \begin{itemize}
            \item Multicore interference results in slowdown of program execution.
            \item Existing tests show slowdown in the ballpark of 300x times slowdown.
            \item These tests rely on designing enemy programs to be run in parallel to the main one.
            \item However, this process of testing is highly manual.
            \item To add, the results may not be reproducible due to lack of parameters to define the testing environment more accurately.
        \end{itemize}

    \end{frame}

    \begin{frame}{Contributions in this work}

        \begin{itemize}
            \item Set of principles of how enemy programs can be evaluated, especially w.r.t. reproducibility.
            \item An auto-tuning framework to automatically refine enemy programs to enable maximum interference.
            \item Experimenting the auto-tuning tool on prior work based enemy programs.
        \end{itemize}
    
    \end{frame}

    
    \begin{frame}{Measuring Interference Reliably}

        Reproducing result of experiment showcasing 300x of slowdown.
        \begin{itemize}
            \item Uncontrolled environment.
            \item Controlled environment.
            \item Statistical refinement. 
        \end{itemize}

        %Add here Fig 1 to explain what each bar in the graph represents.
        %(a) is original experiment result.
        %(b) is result reproduced in uncontrolled environment.
        %(c), (d), (e) is result in a controlled environment (throttling, scaling, fully controlled).
        %(f) statistical approach.

    \end{frame}

    %Uncontrolled environment
    \begin{frame}{Uncontrolled Environment}

    \end{frame}

    %Controlled Environment
    \begin{frame}{Controlled Environment}

        %Several parts to this 
            %Frequency throttling
                %Add Fig 2 to show its effect.
            %Power-save mode by operating system.
            %Cache warmth
            %Thread assignment.
            %Affinity setting.
            %Avoiding pre-emption from OS. 
            %Ensuring parallel execution.
    \end{frame}

    %Statistical refinement
    \begin{frame}

        %Quite a few outlier readings.
        %Mostly due to unforseen circumstances.
        %Percentile method to eliminate outliers.

    \end{frame}

    

\end{document}